Addition and removal energies of circular quantum dots

### 2017-06-14 Manuscript/paper.tex
Unwrap paragraphs
Remove reference to b-hat

Quasidegenerate perturbation theory (QDPT) is an extension to the traditional perturbation theory framework that incorporates multiple reference states.  It provides us with a simple means to extract ground state energies of open-shell systems that are only a few particles away from a closed-shell system.  In particular, it allows us to calculate \textit{addition energies} $\varepsilon_a$ and \textit{removal energies} $\varepsilon_i$ of such systems, which we define as:
\begin{align}
  \varepsilon_a &\equiv E_{\Phi_a} - E_{\Phi}, \\
  \varepsilon_i &\equiv E_{\Phi} - E_{\Phi_i},
\end{align}
where $i$ is restricted to labels of occupied states, $a$ is restricted to labels of unoccupied states, and $|\Phi_p\rangle \equiv \hat b_p |\Phi\rangle$.

>>>>

Quasidegenerate perturbation theory (QDPT) is an extension to the traditional perturbation theory framework that incorporates multiple reference states.  It provides us with a simple means to extract ground state energies of open-shell systems that are only a few particles away from a closed-shell system.  In particular, it allows us to calculate \textit{addition energies} $\varepsilon_a$ and \textit{removal energies} $\varepsilon_i$ of such systems, which we define as:
\begin{align}
  \varepsilon_a &\equiv E_{\Phi_a} - E_{\Phi}, \\
  \varepsilon_i &\equiv E_{\Phi} - E_{\Phi_i},
\end{align}
where $i$ is restricted to labels of occupied states, $a$ is restricted to labels of unoccupied states, $|\Phi_i\rangle \equiv \hat{a}_i^{} |\Phi\rangle$, and $|\Phi_a\rangle \equiv \hat{a}_a^\dagger |\Phi\rangle$.
